Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2018-05-22 theory.tex
change case for model

\subsubsection{Case A}
The tuning method A does not re-optimize $\theta_i$ based on the true flow
enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed assay
($N'$), they do not change from stage to stage. According to equation
\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, when the feed assay ($N$)
changes, then $\beta$ will change accordingly.  This breaks the ideal status of
the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.

@@

\subsubsection{Case B}

@@

\subsubsection{Case C}
The last model assumes that the tail to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such as their product and
$\theta$ remain fixed. 
From equations \eqref{eqs:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:

>>>>

\subsubsection{Model A}
The tuning method A does not re-optimize $\theta_i$ based on the true flow
enrichment. As $\delta U$ and $\alpha$ do not depend on the stage feed assay
($N'$), they do not change from stage to stage. According to equation
\eqref{eq:beta}, when $\alpha$ and $\theta$ are fixed, when the feed assay ($N$)
changes, then $\beta$ will change accordingly.  This breaks the ideal status of
the cascade, i.e.  $N_{i} \neq N'_{i-1} \neq N''_{i+1}$.

@@

\subsubsection{Model B}

@@

\subsubsection{Model C}
The last model assumes that the tail to product enrichment factor remains
constant regardless to the feed assays. To compute the response of the cascade
one need to determine $\alpha$ and $\beta$ such as their product and
$\theta$ remain fixed. 
From equations \eqref{eqs:alphabeta} and the assay conservation equation $N =
\theta N' + (1-\theta)N''$ it is possible to express the product $N'$ as a function of
the feed assay $N$, $\gamma$ and the cut $\theta$ as one solution of the second
order equation \eqref{eq:gamma_p}:
